Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex
It is problematic for us to self-assert the relevance of our own article. Perhaps rephrasing may help to captivate readers' attention.

%************************** Chapters 1 - Introduction **************************
\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
\label{sec:intro}
\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for stock prices. As digitalization is expected to continue in the future, crypotocurrencies will hypothetical get more important. Thus, the topic is characterized as relevant.

>>>>

%************************** Chapters 1 - Introduction **************************
\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
\label{sec:intro}
\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices. As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.
